To Do List

### 2019-05-29 Papers.Rmd
CTCF nearby TAD boundaries note

>>>>

- CTCF showed a remarkable enrichment immediately outside of these boundaries, with sites on the plus strand sharply peaking at upstream TAD boundaries and those on the minus strand peaking at downstream boundaries. Similar enrich- ments at TAD boundaries are observed for RAD21, SMC3 (Cohesin complex), and ZNF143, consistent with previous reports [@Dixon:2012aa][@Zuin:2014aa][@Bailey2015].
